DMTN: Dual-Attention Multi-Task Network for Precise Spatio-Temporal Event Spotting in Volleyball Videos\\

### 2024-11-01 paper.tex
refined title
added figure for kovo dataset

\title{Dual-Attention Network for Precise Temporal and Spatial Event Spotting in Volleyball Videos\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

In volleyball, quick transitions play out in particular regions of the court, making spatial localization just as critical as temporal precision. To address this gap, we introduce a new task: \textit{Precise Spatio-Temporal Event Spotting}, which targets both the exact timing and spatial positioning of key events. This approach, unlike traditional action spotting, aims to provide deeper insights into player positioning and movement patterns, which are essential for analyzing volleyball gameplay.

@@

@@

\begin{figure}[htbp]
    \centerline{\includegraphics{fig1.png}}
    \caption{Model architecture.}
    \label{fig}
\end{figure}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics{fig1.png}}
    \caption{Dual-Attention Feature Aggregation Block.}
    \label{fig2}
\end{figure}

>>>>

\title{DMTN: Dual-Attention Multi-Task Network for Precise Spatio-Temporal Event Spotting in Volleyball Videos\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

In volleyball, quick transitions play out in particular regions of the court, making spatial localization just as critical as temporal precision. To address this gap, we introduce a new task: \textit{Precise Spatio-Temporal Event Spotting} (as depicted in Fig.~\ref{fig-kovo-ex}), which targets both the exact timing and spatial positioning of key events. This approach, unlike traditional action spotting, aims to provide deeper insights into player positioning and movement patterns, which are essential for analyzing volleyball gameplay.

@@

\begin{figure*}[t] 
    \centering
    \includegraphics[width=\textwidth]{figures/fig-kovo-ex.jpg}
    \caption{Example sequence for a spike event, highlighting the exact timing (\(t+3\)) with the spatial location annotated by the white circle and the event class indicated by the text above it.}
    \label{fig-kovo-ex}
\end{figure*}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics{figures/fig1.png}}
    \caption{Model architecture.}
    \label{fig}
\end{figure}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics{figures/fig1.png}}
    \caption{Dual-Attention Feature Aggregation Block.}
    \label{fig2}
\end{figure}
